Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-08-04 article.tex
Add supplement
Using text verbatim from Lisa draft

% ---------------------------------------------------------------------------------------
% BEGIN TITLE AND AUTHORS
% ---------------------------------------------------------------------------------------

\title{Using pressure-driven flow systems to evaluate laser speckle contrast imaging}

@@

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid. A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

The measured noise levels quantified by $u_\textnormal{repeat}$ follow the specifications published by the manufacturers of both flow control systems. This indicates that the stability results shown are typical and representative of actual performance differences. The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which stated that instantaneous flow should be $\pm$2\% from the mean value. The $u_\textnormal{repeat}$ for the pressure-regulated flow system (up to 0.55\%) slightly exceeded the manufacturer's specifications, which indicated that the best stability achievable with this system configuration was $\pm$0.5\% from the mean value. Much larger differences arose from issues with reproducibility and accuracy, with the $u_\textnormal{reproduce}$ and $u_\textnormal{bias}$ of the syringe pump measuring several orders of magnitude higher than those of the pressure-regulated flow system. The syringe pump greatly exceeded the manufacturer's tolerances for both reproducibility ($\pm$0.05\%) and accuracy ($\pm$0.5\%). Corresponding specifications were not available for the pressure-regulated flow system. While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to achieve the stability and reliability seen with the pressure-regulated flow system.

>>>>

% ---------------------------------------------------------------------------------------
% BEGIN TITLE AND AUTHORS
% ---------------------------------------------------------------------------------------
\title{Using pressure-driven flow systems to evaluate laser speckle contrast imaging}

@@

A machined aluminum mold was used to cast the microfluidic as shown in Fig.~\ref{fig:microfluidic}a. The extrusion is 460 $\mu$m $\times$ 460 $\mu$m $\times$ 25 mm, which formed three walls of the channel. The square cross-section (1:1 aspect ratio) roughly matches the circular cross-section of vascular geometries \textit{in vivo}. The PDMS \ce{TiO2} mixture was carefully poured on top of the mold within a polystyrene petri dish and placed in a vacuum chamber to remove air bubbles introduced during pouring. The PDMS was then cured at 70 $^\circ$C for one hour, allowed to cool, and detached from the mold. The microchannel side of the phantom was oxygen plasma bonded to a glass slide to seal the channel. Inlet and outlet ports were attached using 23 gauge blunt tip needles fitted partially inside the phantom, which were epoxied in place for an air-tight seal. Tygon® microbore tubing (0.02$''$ inner diameter, Cole Parmer Instrument Company, LLC.) was connected to the blunt tip ports as inlet and outlet tubing. The inlet tubing was connected to the flow control system using fluidic fittings with FEP tubing (IDEX Health and Science, LLC.). The outlet tubing drained into a vial, with the tubing end fully submerged in liquid (see Supplementary Material S1). A photograph of the phantom is shown in Fig.~\ref{fig:microfluidic}b, where the channel is visible inside the white PDMS with the glass slide sealing the surface.

@@

The measured noise levels quantified by $u_\textnormal{repeat}$ follow the specifications published by the manufacturers of both flow control systems. This indicates that the stability results shown are typical and representative of actual performance differences. The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which state that instantaneous flow should be $\pm$2\% from the mean value. The $u_\textnormal{repeat}$ for the pressure-regulated flow system (up to 0.55\%) slightly exceeded the manufacturer's specifications, which indicated that the best stability achievable with this system configuration was $\pm$0.5\% from the mean value. Much larger differences arose from issues with reproducibility and accuracy, with the $u_\textnormal{reproduce}$ and $u_\textnormal{bias}$ of the syringe pump measuring several orders of magnitude higher than those of the pressure-regulated flow system. The syringe pump greatly exceeded the manufacturer's tolerances for both reproducibility ($\pm$0.05\%) and accuracy ($\pm$0.5\%). Corresponding specifications were not available for the pressure-regulated flow system. While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to ever achieve the stability and reliability seen with the pressure-regulated flow system.
